Stats Project 2

### 2022-12-12 article.Rmd
fixes to article and rough analysis, added log transform to grlivearea in prediction set

We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R^2 compared to the previous non-transformed model. We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic.

@@

ModelRMSE(fit$residuals) #RMSE value of 33802
ModelRMSE(fit_transform$residuals) # RMSE Value of 0.1973
```

>>>>

We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R^2 compared to the previous non-transformed model. We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic. We can also verify from the adjusted $R^2$ and RMSE from each model that the transformed model fits the data much better than the a non-transformed model.

@@

ModelRMSE(fit$residuals) #RMSE value of 33802
ModelRMSE(fit_transform$residuals) # RMSE Value of 0.1973

# Internal CV Press of Models:

train.control1 = trainControl(method = "cv", number = 10)
model1 <- train(SalePrice ~ GrLivArea + Neighborhood + GrLivArea*Neighborhood, data = a1_set, method = "lm", trControl = train.control1)
CVPress(model1$model)# doesn't work atm

### 2022-12-12 rough_analysis.Rmd
fixes to article and rough analysis, added log transform to grlivearea in prediction set

transformed_numeric = numeric_housing
transformed_numeric$SalePrice = log(transformed_numeric$SalePrice)
transformed_numeric$LotArea = log(transformed_numeric$LotArea)

@@

#since the original dataset is transformed, the testset needs to be transformed
#as well to account for the change in base.
test_housing$LotArea = log(test_housing$LotArea)

@@

The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20

>>>>

transformed_numeric = numeric_housing
transformed_numeric$SalePrice = log(transformed_numeric$SalePrice)
transformed_numeric$LotArea = log(transformed_numeric$LotArea)
transformed_numeric$GrLivArea = log(transformed_numeric$GrLivArea)

@@

#since the original dataset is transformed, the testset needs to be transformed
#as well to account for the change in base.
test_housing$LotArea = log(test_housing$LotArea)
test_housing$GrLivArea = log(test_housing$GrLivArea)

@@

The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20141. While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal. This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time. This should be further investigated.
